---
title: "Joe_Rovalino_Data607_proj1"
author: "Joe Rovalino"
date: "9/12/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Install two packages to be used: downloader and Stringr
```{r}
install.packages("downloader")
install.packages("stringr")
```
1) I uploaded the Chess tournament file to my Github directory to connect to web to simulate getting file. Found some documentation on downloader package using instructions:
https://cran.r-project.org/web/packages/downloader/downloader.pdf

```{r}
library(downloader)
url <-"https://raw.githubusercontent.com/jrovalino/jrovalino-Data607-proj1/master/tournamentinfo.txt"
url
#?download
tourfile <- "tournamentinfo.txt"
tourfile
download(url, tourfile)
```

2) Get the stringr library installed 

```{r}
library(stringr)
#?readLines
rslts <- readLines("tournamentinfo.txt")
# Automated data collection in R (ADC in R) chapter 8 - see table 8.3 selected symbols
#wiht special #meaning \w word characters [[:alnum:]_].
# Automated data collection in R (ADC in R) chapter 8 - pg 204 ^ "Putting the former #at the beginning of a character class matches the inverse of the character class' #contents
# another good reference -  #https://stringr.tidyverse.org/articles/regular-expressions.html

pname <- unlist(str_extract_all(rslts, "\\w+[^USCF|a-z]\\w+ \\w+"))
#pname 

pstate<- unlist(str_extract_all(rslts,"[A-Z][A-Z][[ ]][\\|]"))
#pstate
#?str_split simplify = F creates char vector, simplify = True  creates a char matrix
pstate <- str_split(pstate, "[[ ]][\\|]", simplify=TRUE)
#pstate
#only nneed first column in matrix
pstate <- pstate[, 1] 
pstate 
totpts <- unlist(str_extract_all(rslts, "\\d\\.\\d"))
totpts  
prerating <- unlist(str_extract_all(rslts, "[R][:]([[ ]]+)([[:alnum:]]+)", simplify=FALSE))
  #prerating
  prerating <- unlist(str_extract_all(prerating, "([[^R: ]]+[[:alnum:]]+)", simplify=FALSE))
  prerating
  
```
  
#Needed to read some refresher/background on looping and used primarily the text
# https://r4ds.had.co.nz/iteration.html - chapter on iterations

```{r}
#totol number of points (tnop)
#extract round component for each player by leveraging |#.# and greedy quantification #p203 table 8.2 
meanprep<- unlist(str_extract_all(rslts, "\\|[0-9].*"))
meanprep[1]
#need to extract out the opponent #'s to use as an index for later use in getting pre-rating. 
meanprep2 <-unlist(str_replace_all(meanprep, "\\s{1,2}\\|","00|"))
class(meanprep2)
meanprep2[1]
class(meanprep2)
?str_extract_all
#Need to figure out the problem with moving to matrix or to list creating eash
#meanprep3 <- matrix(nrows=7)
meanprep3 <- (str_extract_all(meanprep2, "\\s\\d{1,2}", simplify = TRUE))
meanprep3[1,]
meanprep3 <-gsub('\\s+', '', meanprep3)
meanprep3[1,]

#meanprep3 <- apply(meanprep3, 1, FUN = str_trim)
#meanprep3[1]
ncol(meanprep3)
nrow(meanprep3)
length(meanprep3)
#garbage meancalc <- matrix(unlist(meanprep3), byrow=TRUE,  nrow=ncol(meanprep3) )
#garbade meancalc[1,]

mode(meanprep3) = "numeric"
class( meanprep3 [1, ])
meanprep3 [1, ]

tmean <- meanprep3
tmean

#m <- matrix(unlist(meanprep3), nrow(meanprep3), dimnames = dimnames(meanprep3))
#rowMeans(m)
#data.frame(datamatrix)



#going to use the row and column to populate the matrix so that average can be done.
#class(nrow(tmean))
tmean
nrow(tmean)
ncol(tmean)
is.numeric(tmean[1,1])

for (i in 1:nrow(tmean)) {
  for (j in 1:ncol(tmean)){
    if (tmean[i,j] == 0){tmean[i,j] = NA}
    else{tmean[i,j] <- prerating[tmean[i,j]]}}}


tmean[1,1]
df <- data.frame(pname,pstate, totpts,prerating)
df
# Exporting the result into a CSV file.
write.csv(df, "chesssummary.csv", row.names=FALSE)
  
```
